How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
#new_model_alternative

# Word frequency year
popc <- filter(pop, amazon_speech == 1) %>%
  select(year, text) %>% 
  rename(doc_id = year)
popc$text <- stringr::str_replace_all(popc$text, "meio ambiente", "meioambiente")
popc$text <- stringr::str_replace_all(popc$text, "forcas armadas", "forcasarmadas")
popc$text <- stringr::str_replace_all(popc$text, "estados unidos", "estadosunidos")
popc$text <- stringr::str_replace_all(popc$text, "rio de janeiro", "riodejaneiro")
popc$text <- stringr::str_replace_all(popc$text, "direitos humanos", "direitoshumanos")
popc$text <- stringr::str_replace_all(popc$text, "rio grande do sul", "riograndedosul")
popc$text <- stringr::str_replace_all(popc$text, "copa do mundo", "copadomundo")
popc$text <- stringr::str_replace_all(popc$text, "sao paulo", "saopaulo")
popc$text <- stringr::str_replace_all(popc$text, "rio grande do norte", "riograndedonorte")
popc$text <- stringr::str_replace_all(popc$text, "floresta amazonica", "florestaamazonica")
popc$text <- stringr::str_replace_all(popc$text, "regiao amazonica", "regiaoamazonica")
popc$text <- stringr::str_replace_all(popc$text, "mato grosso|mato-grosso", "matogrosso")
popc$text <- stringr::str_replace_all(popc$text, "minas gerais", "minasgerais")
popc$text <- stringr::str_remove_all(popc$text, " [a-z] ")
popc$text <- tm::removeWords(tm::removePunctuation(popc$text),
                             c(tm::stopwords("pt"), 
                               "nao", "amazonas", "voce", "vao", "dar", "du",
                               "our", "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                               "no", "hoje", "presidente", "governador", 
                               "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                               "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                               "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                               "cumprimentar", "gente", "estado", "querido", "queria",
                               "todos", "companheiro", "senhores", "alguns",
                               "companheiras", "companheiros", "companheira", "entao",
                               "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                               "grosso","ministro", "ministra", "josé", "jose",
                               "palacio", "planalto", "pronunciamento", "sobre",
                               "ministros", "luiz", "disse", "fizemos", "nesse",
                               "antonio", "vou", "eduardo braga", "pais", "coisa",
                               "então", "pouco", "pode", "sera", "dias",
                               "outro", "onde", "discurso", "parte", "fala",
                               "anos", "cada", "todo", "visite site", "disse",
                               "site secretaria", "minas gerais", "lula silva",
                               "inácio lula", "amapa", "bahia", "é", "lá", "et", "in",
                               "httpwwwimprensaplanaltogovbr", "secretaria", "visitesite",
                               "ta", "tudo", "pessoas", "falar", "neves", "tancredo",
                               "brasiliadf", "cardoso", "httpwwwinfoplanaltogovbr", 
                               "sip", "and", "to", "en", "des", "el", "le", "les", "dia",
                               "palavra dorsdne", "fernando henrique", "dorsdne eete",
                               "inacio lula", "lula silva", "inacio", "republica",
                               "quegente", "muitas vezes", "ainda", "realmente",
                               "assim", "possa", "coisas", "apenas", "acho", "ano",
                               "vez", "portanto", "todas", "questao", "lado", "outros",
                               "prezado", "vem", "sempre", "sarney", "luis", "serao", 
                               "tao", "meses", "quase", "diante", "brasil", "sendo",
                               "rsdneennoerqe", "brasil", "neste", "digo", "quase", 
                               "queremos", "nesse", "nessa", "mim", "eete", "obrigado", "muita"))
popc <- tm::VCorpus(tm::DataframeSource(popc))
popn <- tidytext::tidy(popc) %>%
  unnest_tokens(word, text) %>% 
  group_by(id, word) %>% 
  summarise(count = n()) %>% 
  arrange(-count) %>% 
  slice(1:10)
popn <- aggregate(popn$word, list(popn$id), paste, collapse=", ") %>% 
  rename(Year = "Group.1", Terms = "x")
tibble(popn)
##### LDA per year just in case
pop_dtm  <- DocumentTermMatrix(popc)
pop_lda <- topicmodels::LDA(pop_dtm, k = 10, control = list(seed = 1234))
pop_lday <- tidy(pop_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:1) %>% # get the top 3 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 1)) %>%
  distinct() %>% 
  rename (Year = document)
pop_10 <- tidy(pop_lda, matrix = "beta") %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  filter(row_number() %in% 1:10) %>%
  arrange(topic)
pop_10 <- aggregate(pop_10$term, list(pop_10$topic), paste, collapse=", ") %>%
  rename(topic = "Group.1", Terms = "x")
popt <- dplyr::left_join(pop_10, pop_lday, by = "topic") %>%
  select(Year, Terms) %>% 
  arrange(Year)
tibble(popt)

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# model
model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)
# summary statistics
stargazer::stargazer(model, type = "text")
# Plot model
ama_model$predicted = predict(model, ama_model, type = "response")
ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
  geom_smooth(size = .5, color = "darkgreen") +
    labs(x = "Distance to Manaus (km)",
       y = "Environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))

>>>>

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# model

model_logit <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,family=binomial(link = "logit"), data = ama_model)

model_lm <- lm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI, data = ama_model)

# summary statistics
stargazer::stargazer(model_lm, type = "text")

plot_model(model_lm)
summary(model_lm)

# Plot model

ama_model$predicted = predict(model_lm, ama_model, type = "response")
ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
  geom_jitter(alpha=.5)+
  geom_smooth(size = .5, color = "darkgreen") +
    labs(x = "Distance from the Amazon (km)",
       y = "Share of environmental conservation",
       title = "Amazon constructions as an issue of  environmental conservation\nin relation to distance from the Amazon",
       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
